A systematic search for transiting planets in the \KT\ data

### 2015-02-16 ms.tex
to do comment-done
Difference imaging centroid citation

In \KT, the precision of these tests is lower and they must be applied with
care.
There are typically only a handful of transits, meaning differences between
``odd'' and ``even'' transits must be large to create a significant
difference.
Searching for ellipsoidal variations is hindered by the short time baseline
and the increased photometric uncertainty in \KT\ data.
Centroid variations are feasible in \KT\ but must be treated differently than
in the original \kepler\ mission where this effect was generally measured
using difference imaging \dfmtodo{(cite)}.

@@

\begin{table}[p]
\begin{center}
\small
\include{tab-cand}
\end{center}
\caption{%
The catalog of planet candidates and their observable properties.
These values and their uncertainties are derived from MCMC samplings and the
numbers are computed as the 0.16, 0.5, and 0.84 posterior sample quantiles.
\dfmtodo{RA/Dec coords.}
\tablabel{cand}}
\end{table}

>>>>

In \KT, the precision of these tests is lower and they must be applied with
care.
There are typically only a handful of transits, meaning differences between
``odd'' and ``even'' transits must be large to create a significant
difference.
Searching for ellipsoidal variations is hindered by the short time baseline
and the increased photometric uncertainty in \KT\ data.
Centroid variations are feasible in \KT\ but must be treated differently than
in the original \kepler\ mission where this effect was generally measured
using difference imaging \citep{Batalha:2010}.

@@

\begin{table}[p]
\begin{center}
\small
\include{tab-cand}
\end{center}
\caption{%
The catalog of planet candidates and their observable properties.
These values and their uncertainties are derived from MCMC samplings and the
numbers are computed as the 0.16, 0.5, and 0.84 posterior sample quantiles.
\tablabel{cand}}
\end{table}
